---
title: "Latency and capacity estimation for a network connection from asymmetric measurements"
output: html_document
---

## First Dataset

1- Preparing the Data 

uploading the Data 
```{r}
library(dplyr)
df = read.table('liglab2.log', sep=' ' , na.strings =""  , header=F , fill = TRUE  )
```



Selecting the usefull columns for our Analysing
```{r}
df = df %>% select(V1, V2, V9) 
```



Elemenating the lines with no available data
```{r}
library(tidyr)
line_NA  = apply(df , 1 , function(x) any(is.na(x)))
df = df %>% drop_na()
```


Change the name of columns
```{r}
colnames(df)=c('date' ,'size' , 'time' )
```



Convert Time 
```{r}
convertTime = function(time)
  gsub("[^0-9.]", "", time)

df$time = as.numeric(sapply(df$time , convertTime))
```



Convert Date 
```{r}
convertdate = function(date)
  gsub("[^0-9.]", "", date)


df$date = as.numeric(sapply(df$date , convertdate))
```


Ploting the Data 
```{r}
head(df)
plot(time~size,df, main="Ploting the time as a function of the packets size", col="brown4")
```



Calculating the means 
```{r}
mean.size = mean(df$size)
mean.time = mean(df$time)

mean.size
mean.time
```


Ploting The mean 
```{r}
plot(time~size,df)
abline(h=mean.time,col="Yellow")
```

Ploting the linear regression with the mean
```{r}
plot(time~size,df)
mode=lm(time~size,df)
abline(mode,col="red")
abline(h=mean.time,col="Yellow")

```



The intercept of the mode 
```{r}
mode
```


The summary of the mode 
```{r}
summary(mode1)
```



Deviding Data 

the first interval 
```{r}
library(ggplot2)
df1 = subset(df,size<=1480&size>=0)
ggplot(data = df1, mapping = aes(x = size, y = time)) +geom_point(color="brown4") + geom_smooth(method='lm', color= "red") + theme_bw() + coord_cartesian(ylim = c(0.25,7)) + ggtitle("The time as function of the size (size < 1480)")

```
```{r}
mode1 <- lm(data=df1, time~size)
par(mfrow=c(2,2)); plot(mode1); par(mfrow=c(1,1))
```



The second interval

```{r}
df2 = subset(df,size>1480)
ggplot(data = df2, mapping = aes(x = size, y = time)) +geom_point(color="brown4") + geom_smooth(method='lm', color= "red") + theme_bw() +
  ggtitle("The time as function of the size (size > 1480)")
```
```{r}
mode2 <- lm(data=df2, time~size)
par(mfrow=c(2,2)); plot(mode2); par(mfrow=c(1,1))
```


The two modes
```{r}
mode1
mode2
```


The summary of the two modes 
```{r}
summary(mode1)
summary(mode2)
```


subploting both 
```{r}
ggplot(data = df, mapping = aes(x =size, y = time)) + geom_point(col="brown4")+ geom_smooth(method='lm', data=df1, color= "black")+ geom_smooth(method='lm', data=df2, color= "yellow") + ggtitle("Superposing the results")
```





Diffrent Approach 1 : Taking the minimum time per message size 


```{r}
df_min = unique(aggregate(time~size,df,min))
df1_min = unique(aggregate(time~size,df1,min))
ggplot(data = df1_min, mapping = aes(x = size, y = time)) +geom_point(color="brown4") + geom_smooth(method='lm', color= "red") + theme_bw()+
  ggtitle("Linear regression for the size < 1480")

```



```{r}
df2_min = unique(aggregate(time~size,df2,min))
ggplot(data = df2_min, mapping = aes(x = size, y = time)) +geom_point(color="brown4") + geom_smooth(method='lm', color= "red") + theme_bw() + 
ggtitle("Linear regression for the size > 1480")
```

```{r}
mode1_min <- lm(data=df1_min, time~size)
par(mfrow=c(2,2)); plot(mode1_min); par(mfrow=c(1,1))
```

```{r}
mode2_min <- lm(data=df2_min, time~size)
par(mfrow=c(2,2)); plot(mode2_min); par(mfrow=c(1,1))
```
```{r}
summary(mode1_min)
```

```{r}
summary(mode2_min)
```

subploting both 
```{r}
ggplot(data = df_min, mapping = aes(x =size, y = time)) + geom_point(col="brown4")+ geom_smooth(method='lm', data=df1_min, color= "black")+ geom_smooth(method='lm', data=df2_min, color= "yellow") + ggtitle("Superposing the results")
```

Diffrent Approach 2 : Taking the minimum time per message size

```{r}
q10 <- seq(0, 1, by = 0.1)
ggplot(data = df1, mapping = aes(x = size, y = time)) +
  geom_point(color="brown4") + 
  geom_smooth(method='lm', color= "red") + theme_bw() +
  geom_quantile (quantiles = q10, color="blue")+
  ggtitle("Quantile regression for the size < 1480")
```

```{r}
q10 <- seq(0, 1, by = 0.1)
ggplot(data = df2, mapping = aes(x = size, y = time)) +
  geom_point(color="brown4") + 
  geom_smooth(method='lm', color= "red") + theme_bw() +
  geom_quantile (quantiles = q10, color="blue") +
  ggtitle("Quantile regression for the size > 1480")
  
```





#### SECOND DATASET 
```{r}
df_1 = read.table('stackoverflow.log', sep=' ' , na.strings =""  , header=F , fill = TRUE  )
```

Clean the data: 
```{r}
df_1 = df_1 %>% select(V1, V2, V9) 
library(tidyr)
line_NA  = apply(df_1 , 1 , function(x) any(is.na(x)))
df_1 = df_1 %>% drop_na()
colnames(df_1)=c('date' ,'size' , 'time' )
convertdate = function(date)
  gsub("[^0-9.]", "", date)


df_1$date = as.numeric(sapply(df_1$date , convertdate))

convertTime = function(time)
  gsub("[^0-9.]", "", time)

df_1$time = as.numeric(sapply(df_1$time , convertTime))
```

Plot the data
```{r}
head(df_1)
plot(time~size,df_1, main="Ploting the time as a function of the packets size", col="brown4")
```


Deviding Data 
```{r}
library(ggplot2)
df_1.1 = subset(df_1,size<=1480&size>=0)
ggplot(data = df_1.1, mapping = aes(x = size, y = time)) +geom_point(color="brown4") + geom_smooth(method='lm', color= "red") + theme_bw()  + ggtitle("The time as function of the size (size < 1480)")
```

```{r}
df_1.2 = subset(df_1,size>1480)
ggplot(data = df_1.2, mapping = aes(x = size, y = time)) +geom_point(color="brown4") + geom_smooth(method='lm', color= "red") + theme_bw() +
  ggtitle("The time as function of the size (size > 1480)")
```

Checking the hypthesis
```{r}
mode_1.1 <- lm(data=df_1.1, time~size)
par(mfrow=c(2,2)); plot(mode_1.1); par(mfrow=c(1,1))
```
```{r}
mode_1.2 <- lm(data=df_1.2, time~size)
par(mfrow=c(2,2)); plot(mode_1.2); par(mfrow=c(1,1))
```


Checking the model 
```{r}
summary(mode_1.1)
summary(mode_1.2)
```

subploting both 
```{r}
ggplot(data = df_1, mapping = aes(x =size, y = time)) + geom_point(col="brown4")+ geom_smooth(method='lm', data=df_1.1, color= "black")+ geom_smooth(method='lm', data=df_1.2, color= "yellow") + ggtitle("Superposing the results")
```


Diffrent Approach 1 : Taking the minimum time per message size 


```{r}
df_1.1_min = unique(aggregate(time~size,df_1.1,min))
ggplot(data = df_1.1_min, mapping = aes(x = size, y = time)) +geom_point(color="brown4") + geom_smooth(method='lm', color= "red") + theme_bw()+ coord_cartesian(ylim = c(110,115))+
  ggtitle("Linear regression for the size < 1480")
```
```{r}
df_1.2_min = unique(aggregate(time~size,df_1.2,min))
ggplot(data = df_1.2_min, mapping = aes(x = size, y = time)) +geom_point(color="brown4") + geom_smooth(method='lm', color= "red") + theme_bw() + coord_cartesian(ylim = c(110,120)) +
ggtitle("Linear regression for the size > 1480")
```

checking the hypothesis
```{r}
mode_1.1_min <- lm(data=df_1.1_min, time~size)
par(mfrow=c(2,2)); plot(mode_1.1_min); par(mfrow=c(1,1))
```
```{r}
mode_1.2_min <- lm(data=df_1.2_min, time~size)
par(mfrow=c(2,2)); plot(mode_1.2_min); par(mfrow=c(1,1))
```


cheking the model 
```{r}
summary(mode_1.1_min)
summary(mode_1.2_min)
```

