---
title: "Latency and capacity estimation for a network connection from asymmetric measurements"
output: html_document
---

## First Dataset

1- Preparing the Data 

uploading the Data 
```{r}
library(dplyr)
df = read.table('liglab2.log', sep=' ' , na.strings = ""  , header=F , fill = TRUE  )
```



Selecting the usefull columns for our Analysing
```{r}
df = df %>% select(V1, V2, V9) 
```



Elemenating the lines with no available data
```{r}
library(tidyr)
line_NA  = apply(df , 1 , function(x) any(is.na(x)))
df = df %>% drop_na()
```


Change the name of columns
```{r}
colnames(df)=c('date' ,'size' , 'time' )
```



Convert Time 
```{r}
convertTime = function(time)
  gsub("[^0-9.]", "", time)

df$time = as.numeric(sapply(df$time , convertTime))
```



Convert Date 
```{r}
convertdate = function(date)
  gsub("[^0-9.]", "", date)


df$date = as.numeric(sapply(df$date , convertdate))
```


Ploting the Data 
```{r}
plot(time~size,df)
```



Calculating the means 
```{r}
mean.size = mean(df$size)
mean.time = mean(df$time)

mean.size
mean.time
```


Ploting The mean 
```{r}
plot(time~size,df)
abline(h=mean.time,col="Yellow")
```

Ploting the linear regression with the mean
```{r}
plot(time~size,df)
mode=lm(time~size,df)
abline(mode,col="red")
abline(h=mean.time,col="Yellow")

```



The intercept of the mode 
```{r}
mode
```


The summary of the mode 
```{r}
summary(mode1)
```



Deviding Data 

the first interval 
```{r}
df1 = subset(df,size<=1480&size>=0)
plot(time~size,df1)
mode1=lm(time~size,df1)
abline(mode1,col="red")
```

The second interval

```{r}
df2 = subset(df,size>1480)
plot(time~size,df2)
mode2=lm(time~size,df2)
abline(mode2,col="red")
```


The two modes
```{r}
mode1
mode2
```


The summary of the two modes 
```{r}
summary(mode1)
summary(mode2)
```


subploting both 
```{r}
library(ggplot2)
library("quantreg")
library(SparseM)

p <- ggplot(data = df, mapping = aes(x =size, y = time))+
geom_point() + geom_quantile(quantiles = 0.85, data=subset(df, size >= 1480), colour = "red", size = 2) +
geom_quantile(quantiles = 0.85, data=subset(df, size < 1480), colour = "blue", size = 2)
p
```



